\chapter{\label{cha:Preface}Preface}

This document describes the project I have done for my final exam for the MSc (Laurea Specialistica) in Computer Engineering at University of Bologna. The research was performed at the Parallel and Distributed System Group of the Faculty Electrical Engineering, Mathematics, and Computer Science of Delft University of Technology. I was there from October 2008 to April 2009 as exchange student participating to the LLP Erasmus 2008/2009. I would like to thank Prof.ssa ing.~Eleonora Franchi Scarselli who was promoter and coordinator of the exchange.

During those months I worked under supervision of Dr.\ ir.~Johan Pouwelse. He is assistant professor at Delft University of Technology and the scientific director of the P2P-Next European project investigating the next-generation of peer-to-peer technology. I would like to thank him for his contribution, his contagious enthusiasm and for changing my recurring overuse of bottom-up approach to problem solving.

I took advantages in working with Ph.D.~Tam\'{a}s Vink\'{o}, who is expert in global optimization, and Ph.D.~David Hales, who is a computational social scientist. I would like to thank them for our perceptive discussions and their pointers.

I would like to thank my supervisor at University of Bologna, Prof.\ ing.~Paolo Ciaccia, for having reviewed this work and for participating in the examination committee.

Finally I would like to thank ir.~Frank Mulder for all countless tips he gave me, ir.~Riccardo Petrocco and ir.~Diego Rabaioli for their technical support.

\vskip1cm
\begin{flushright}
\theauthor\\

Bologna, \today\\
\end{flushright}
